Analysis

### 2022-05-28 analysis/analysis.Rmd
included Jans latest suggestions

popdens_plot <- ggplot(all_proxies_orig) +
  geom_line(aes(x = (1950-age) * -1, y = scale(openness), col="Openness Indicator")) +
  geom_line(aes(x = (1950-age) * -1, y = scale(sumcal), col="Sum Calibration")) +
  geom_line(aes(x = (1950-age) * -1, y = scale(dendro), col="Dendro Dated Settlements")) +
  geom_line(aes(x = (1950-age) * -1, y = scale(aoristic_sum), col="Aoristic Sum")) +
  geom_line(data = PopDens_summary,
            aes(x = (1950-age) * -1, y=mean, col = "Estimation Result")) + 
  geom_line(data = PopDens_summary,
            aes(x = (1950-age) * -1, y=hpdi_l, col = "Estimation Result"), lty=2) + 
  geom_line(data = PopDens_summary,
            aes(x = (1950-age) * -1, y=hpdi_u, col = "Estimation Result"), lty=2) +
  theme_minimal() + scale_x_reverse() + 
  scale_colour_manual(
    values = c("Openness" = "darkgreen",
               "Sum Calibration" = "red",
               "Aoristic Sum" = "gray",
               "Dendro Dated Settlements" = "brown",
               "Estimation" = "black"), name = "") +
  theme(legend.position="bottom") +
  ylab("Scaled values for Proxies,\n P/km² for Estimation") +
  xlab("cal BCE")
popdens_plot
```

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","popdens_estimation.pdf"), mustWork = F),
       plot = popdens_plot, width = 21, height = 29.7/2, units = "cm")
```

>>>>

proxies_and_result <- rbind(melt(all_proxies_orig, id.vars = "age"),
                            melt(PopDens_summary[,2:5], id.vars = "age")
)

variable_full_name = c(
      sumcal = "Sum Calibration",
      openness = "Openness",
      aoristic_sum = "Aoristic Sum",
      dendro = "Dendro Dated Settlements",
      mean = "Estimation"
      )

popdens_plot <- ggplot() +
  geom_line(data = subset(
    proxies_and_result,
    variable %in% c("mean",
                    "openness",
                    "sumcal",
                    "dendro",
                    "aoristic_sum")
    ),
    aes(x = (1950-age) * -1, y = value, color = variable)) +
    geom_ribbon(data = subset(
      proxies_and_result,
      variable %in% c("mean")
      ),
      aes(x = (1950-PopDens_summary$age) * -1,
          ymin = PopDens_summary$hpdi_l,
          ymax = PopDens_summary$hpdi_u),
      fill = "grey70", alpha = 0.5) +
  facet_wrap(. ~ variable,
             scales="free_y",
             ncol = 1,
             labeller = labeller(variable = variable_full_name)) +
  theme_minimal() + scale_x_reverse() + theme(legend.position="false") +
  ylab("Scaled values for Proxies,\n P/km² for Estimation") +
  xlab("cal BCE") + 
  scale_colour_manual(
    values = c("sumcal" = "red",
      "openness" = "darkgreen",
               "Aoristic Sum" = "gray",
               "dendro" = "brown",
               "mean" = "black")
    )

popdens_plot_adjusted <- ggplotGrob(popdens_plot)

popdens_plot_adjusted$heights[[28]] <- unit(4, 'null')

grid.newpage()
grid.draw(popdens_plot_adjusted)
```

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","popdens_estimation.pdf"), mustWork = F),
       plot = popdens_plot_adjusted, width = 21, height = 29.7/2, units = "cm")
```
